### 2020-04-14 intro.tex
readded sections with modified pdfs
Cleaning up.

\section{Introduction}
\label{sec:intro}
The Cray XK7 Titan supercomputer was the \#1 system in the world for a
very long time, and has remained a critically important computer
system through the end of its life in the Summer of 2019. It defied
scale with 18,688 individual compute nodes and delivered tens of
billions of computing hours to the U.S. Oepartment of Energy
mission-critical programs for nearly 7 years.

@@

Figure~\ref{fig:chronology} illustrates the chronology of the rework
cycles. It shows the number of GPU changes at periodic inventories.
\begin{figure}[htbp]
  \centering
  \includegraphics[width=\textwidth]{figs/chronology.pdf}
  \caption{Daily volume of GPU swaps with labels on most frequent dates.}
  \label{fig:chronology}
\end{figure}

>>>>

% !TEX root = main.tex
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Introduction
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Introduction}
\label{section:introduction}

The Cray XK7 Titan supercomputer was the \#1 system in the world for a
very long time, and has remained a critically important computer
system through the end of its life in the Summer of 2019. It defied
scale with 18,688 individual compute nodes and delivered tens of
billions of computing hours to the U.S. Oepartment of Energy
mission-critical programs for nearly 7 years.

@@

Figure~\ref{fig:chronology} illustrates the chronology of the rework
cycles. It shows the number of GPU changes at periodic inventories.
\begin{figure*}[tbp]
  \centering
  \includegraphics[width=\textwidth]{figs/chronology001.pdf}
  \caption{Daily volume of GPU swaps with labels on most frequent dates.}
  \label{fig:chronology}
\end{figure*}
